Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-04-29 tex/paper1/paper1.tex
paper edits

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{jack.ireland@nasa.gov}
\newcommand{\Fps}{Fourier power spectrum}

@@

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eq:pwrlaw}
P_{0}(f) = Af^{-n} + C,
\end{equation}
where $A>0$ is a proportionality constant, $n>0$ is the power law
index, and $C>0$ describes the high-frequency Fourier power.

@@

\subsection{Nature of the power law power spectrum}\label{ssec:nplps}

>>>>

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{jack.ireland@nasa.gov}
\newcommand{\PS}{power spectrum}
\newcommand{\PL}{power-law}
\newcommand{\Fps}{Fourier \PS}

@@

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eq:pwrlaw}
P_{0}(f) = Af^{-n} + C,
\end{equation}
where $A>0$ is a proportionality constant and $n>0$ is the power law
index.  The quantity $C>0$ models the high-frequency / low power end
of the spectrum where the detection properties of the detector
apparatus are assumed to dominate the observations.

@@

\subsection{Nature of the power law power spectrum}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
red-noise like power spectrum.  It is present in both wavebands
studied and in all the regions, and so parsimony suggests that the
mechanism of its creation is both similar and ubiquitous in all parts
of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
the sum of a distribution of a large number of energy deposition
events having different energies. \cite{} describes how a
\PL\ \PS\ may obtained from such a distribution, and that argument
outlined below.

Each energy deposition event is modeled as an exponentially decaying
function of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = E \frac{1}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(f) = E\frac{1}{1 + (2\pi f T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:ftexpdecay}
P_{T}(f) = \sum_{T}N(T)P_{T}(f)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
energy $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the energy in each event depends on its time scale $T$ such that
\begin{equation}
\label{eqn:energydistrib}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown \cite{} that the observed power spectrum can be
approximated by
\begin{equation}
\label{eqn:energydistrib}
P(f) \propto f^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}

This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar events.  The detailed
application of this model of the observed background \PL\ power
spectra will depend strongly on three factors that influence the
observation.  Firstly, the distribution of events along the line of
sight and their temporal dependence (expressed through the parameters
$\alpha_{E}$ and $\gamma$ in Equation \ref{eqn:energydistrib}) have
strong effects on the observed \Fps.  Secondly, the physics of the
radiation emitted as a function of the energy deposited in each event
and the existing plasma properties must be consistently modeled.
Finally, the properties of the observing instrument, in this case the
AIA filters, will also influence the observed \Fps.  These three
factors must be modeled in order to confirm or deny the hypothesis
that ubiquitous energy deposition events are the root cause of the
observed Fourier power spectra.
